NLTK: The Natural Language Toolkit

### 2002-03-29 technical/acl2002/submission.tex
- Very minor tweaks
svn/trunk@532

\documentclass[11pt]{article}
\usepackage{acl02sub,url,alltt,epsfig}
\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science and Linguistic Data Consortium\\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\summary{%
NLTK, the Natural Language Toolkit, is a suite of program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learning structured
programming by example, and manipulating sophisticated models from the
outset.}

\paperid{Pxxxx}
\keywords{teaching, courseware, Python, corpora}
\contact{Edward Loper}
\conference{this paper has not been submitted to any other conferences}
\date{\today}

@@

% To do:
%   - Write up other approaches
%   - General clean-up
% We assume that the user is familiar with the acronym ``NLP;'' is
% that ok?

@@

\paragraph{\textit{Ease of Use.}} The primary purpose of the toolkit is
to allow students to concentrate on building NLP systems.  The more
time students must spend learning to use the toolkit, the less useful
it is.

@@

\textit{This section will include a discussion of other approaches to
implementing computational linguistics courseware, including
\emph{Programming for Linguistics: Java Technology for Language
Researchers}\cite{Hammond02} and \emph{the OpenNLP project}\cite{opennlp}.}

>>>>

%
% Submission for ``Effective Tools And Methodologies For Teaching
% Natural Language Processing And Computational Linguistics'' workshop
% at ACL 2002
%
% Authors: Edward Loper and Steven Bird
% 
% $Id$
%
\documentclass[11pt]{article}
\usepackage{acl02sub,url,alltt,epsfig}
\title{NLTK: The Natural Language Toolkit}
\author{
Edward Loper and Steven Bird\\
Department of Computer and Information Science and Linguistic Data Consortium\\
University of Pennsylvania, Philadelphia, PA 19104-6389, USA
}
\summary{%
NLTK, the Natural Language Toolkit, is a suite of program modules,
tutorials and problem sets, providing ready-to-use computational
linguistics courseware.  NLTK covers symbolic and statistical natural
language processing, and is interfaced to annotated corpora.  Students
augment and replace existing components, learning structured
programming by example, and manipulating sophisticated models from the
outset.}

\paperid{Pxxxx}
\keywords{teaching, courseware, Python, corpora}
\contact{Edward Loper}
\conference{this paper has not been submitted to any other
conferences}
% In the submission example, they had \date{}; but \date{\today} is
% helpful when printing draft copies, to keep track of versions.
%\date{\today}
\date{}

@@

% To do:
%   - Write up other approaches
% We assume that the user is familiar with the acronym ``NLP;'' is
% that ok?

@@

\paragraph{\textit{Ease of Use.}} The primary purpose of the toolkit is
to allow students to concentrate on building natural language
processing (NLP) systems.  The more time students must spend learning
to use the toolkit, the less useful it is.

@@

This section will include a discussion of other approaches to
implementing computational linguistics courseware, including
\emph{Programming for Linguistics: Java Technology for Language
Researchers}\cite{Hammond02} and \emph{the OpenNLP
project}\cite{opennlp}.
